---
title: "Chevron Catalog"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Chevron Catalog}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options:
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(dplyr)
library(dunlin)
library(chevron)
```

## **TABLES**

### **Safety Summary (`AET01`)**

#### **1. Safety Summary**

The **`aet01`** template produces the standard safety summary.

```{r}
run(aet01, syn_data, arm_var = "ARM")
```

#### **2. Safety Summary with Modified Rows**

Analyses under "Total number of patients with at least one" can be removed, added, or modified by editing the parameter `anl_vars`. An analyses here is an abbreviated name of the analyses of interest, and supported by a variable in `ADAE` derived under the condition of interest. The defined analyses currently include `"FATAL"`, `"SER"`, `"SERWD"`, `"SERDSM"`, `"RELSER"`, `"WD"`, `"DSM"`, `"REL"`, `"RELWD"`, `"RELDSM"`, and `"SEV"`. When modification is made, analyses must be all listed in the parameter `anl_vars`. The example below shows adding customized analyses `"RELCTC35"`.

```{r}
proc_data <- syn_data
proc_data$adae <- proc_data$adae %>%
  filter(.data$ANL01FL == "Y") %>%
  mutate(
    FATAL = with_label(.data$AESDTH == "Y", "AE with fatal outcome"),
    SER = with_label(.data$AESER == "Y", "Serious AE"),
    SEV = with_label(.data$ASEV == "SEVERE", "Severe AE (at greatest intensity)"),
    REL = with_label(.data$AREL == "Y", "Related AE"),
    WD = with_label(.data$AEACN == "DRUG WITHDRAWN", "AE leading to withdrawal from treatment"),
    DSM = with_label(
      .data$AEACN %in% c("DRUG INTERRUPTED", "DOSE INCREASED", "DOSE REDUCED"),
      "AE leading to dose modification/interruption"
    ),
    SERWD = with_label(.data$SER & .data$WD, "Serious AE leading to withdrawal from treatment"),
    SERDSM = with_label(.data$SER & .data$DSM, "Serious AE leading to dose modification/interruption"),
    RELSER = with_label(.data$SER & .data$REL, "Related Serious AE"),
    RELWD = with_label(.data$REL & .data$WD, "Related AE leading to withdrawal from treatment"),
    RELDSM = with_label(.data$REL & .data$DSM, "Related AE leading to dose modification/interruption"),
    CTC35 = with_label(.data$ATOXGR %in% c("3", "4", "5"), "Grade 3-5 AE"),
    CTC45 = with_label(.data$ATOXGR %in% c("4", "5"), "Grade 4/5 AE"),
    RELCTC35 = with_label(.data$ATOXGR %in% c("3", "4", "5") & .data$AEREL == "Y", "Related Grade 3-5")
  )

proc_data$adsl <- proc_data$adsl %>%
  mutate(DCSREAS = reformat(.data$DCSREAS, missing_rule))

run(aet01, proc_data, anl_vars = list(safety_var = c("FATAL", "SER", "RELSER", "RELCTC35")), auto_pre = FALSE)
```

### **Safety Summary (Adverse Events of Special Interest) (`AET01_AESI`)**

#### **1. Safety Summary (Adverse Events of Special Interest)**

The **`aet01_aesi`** template produces the standard safety summary for adverse events of special interest.

```{r}
run(aet01_aesi, syn_data)
```

#### **2. Safety Summary (Adverse Events of Special Interest) (optional lines)**

Additional analyses can be added with the parameter `aesi_vars`, please type `?aet01_aesi` in console to find out the list of all pre-defined optional analyses in the HELP.

```{r}
run(aet01_aesi, syn_data, aesi_vars = c("RESLWD", "RELSER"))
```

#### **3. Safety Summary (Adverse Events of Special Interest) (for studies with multiple drugs)**

For studies with more than one study drug, users need to define the analyses in `adae` and add to the parameter `aesi_vars` following the example above. No pre-defined analyses is available at this moment. 

### **Adverse Events (`AET02`)**

#### **1. Adverse Events**

1) The template `aet02` produces the standard adverse event summary by MedDRA system organ class and preferred term.
2) The template does not include the column of total as default. The 'All Patients' column can be added by `lbl_overall = "All Patients"`.
3) Missing values in `"AEBODSYS"`, and `"AEDECOD"` are labeled by `No Coding Available`.

```{r}
run(aet02, syn_data)
```

#### **2. Adverse Events (with High-level Term)**

The syntax below displays adverse events by MedDRA system organ class, high-level term and preferred term.

```{r}
run(aet02, syn_data, row_split_var = c("AEBODSYS", "AEHLT"))
```

#### **3. Adverse Events (Preferred Terms only)**

The syntax below displays adverse events by preferred term only.

```{r}
run(aet02, syn_data, row_split_var = NULL)
```

### **Adverse Events by Greatest Intensity(`AET03`)**

#### **1. Adverse Events by Greatest Intensity**

This **`aet03`** template  produces the standard adverse event by greatest intensity summary

```{r}
run(aet03, syn_data)
```

### **Adverse Events by Highest `NCI CTCAE` Grade (`AET04`)**

#### **1. Adverse Events by Highest `NCI CTCAE` Grade**

1) The **`aet04`** template produces the standard adverse event by highest `NCI CTCAE` grade summary.  
2) By default, this template includes the grouped grades of 'Grade 1-2' and 'Grade 3-4'.   
3) By default this template removes the rows with 0 count.   
4) If a treatment group does not have any adverse event, the treatment group is automatically displayed providing that it is defined in `ADSL`.

```{r}
run(aet04, syn_data)
```

#### **2. Adverse Events by Highest `NCI CTCAE` Grade (Fill in of Grades)**

If for some preferred terms not all grades occur but all grades should be displayed, this can be achieved by specifying `prune_0 = FALSE`.

```{r}
run(aet04, syn_data, prune_0 = FALSE)
```

#### **3. Adverse Events by Highest `NCI CTCAE` Grade with modified grouping of grade**

To collapse grade 3-4 with grade 5, this can be achieved by modifying the definition of grade groups in `grade_groups`.

```{r}
grade_groups <- list(
  "Grade 1-2" = c("1", "2"),
  "Grade 3-5" = c("3", "4", "5")
)

run(aet04, syn_data, grade_groups = grade_groups, prune_0 = FALSE)
```

### **Most Common (>=5%) Adverse Events (`AET05`)**

#### **1. Most Common (>=5%) Adverse Events**

1) The **`aet10`** template produces the standard most common adverse events occurring with relative frequency >=5% output.

```{r}
run(aet10, syn_data)
```

#### **2. Most Common (>=8%) Adverse Events (setting threshold)**

To modify the threshold for displaying preferred terms, this can be achieved by providing the threshold to the `atleast` parameter.  

```{r}
run(aet10, syn_data, atleast = 0.08)
```

### **Concomitant Medications by Medication Class and Preferred Name (`CMT01A`)**

#### **1. Concomitant Medications by Medication Class and Preferred Name**

1) The **`cmt01a`** template displays concomitant medications by `ATC Level 2` and Preferred Name by default.  
2) The template does not include the column of total by default.  
3) The template sort medication class and preferred name by alphabetical order by default.  

```{r}
run(cmt01a, syn_data)
```

#### **2. Concomitant Medications by Medication Class and Preferred Name (changing `ATC class level`)**

```{r}
run(cmt01a, syn_data, row_split_var = "ATC1")
```

#### **3. Concomitant Medications by Medication Class and Preferred Name (classes sorted by frequency)**

The option `sort_by_freq = TRUE` sort medication class by frequency.

```{r}
run(cmt01a, syn_data, sort_by_freq = TRUE)
```

#### **4. Concomitant Medications by Medication Class and Preferred Name (total number of treatments per medication class suppressed)**

The **`cmt01a`** template includes the analysis of 'total number of treatments' by default, modify `summary_labels` to change it.

```{r}
#run(cmt01a, syn_data, summary_labels = list(TOTAL = cmt01_label, ATC2 = cmt01_label[1]))
```

### **Concomitant Medications by Preferred Name (`CMT02_PT`)**

#### **1. Concomitant Medications by Preferred Name**

1) The **`cmt02_pt`** template displays concomitant medications by Preferred Name by default.  
2) The template does not include the column of total by default.  
3) The template sorts preferred name by alphabetical order by default. Set the option `sort_by_freq = TRUE` to sort preferred names by frequency.  

```{r}
run(cmt02_pt, syn_data)
```

### **Demographics and Baseline Characteristics (`DMT01`)**
  
#### **1. Demographics and Baseline Characteristics with All Patients**

1) The **`dmt01`** template produces the standard demographics and baseline characteristics summary.  
2) This template includes the column of total by default.  

```{r}
run(dmt01, syn_data)
```

#### **2. Demographics and Baseline Characteristics without All Patients**

To remove the column of total, set the parameter `lbl_overall` to `NULL`. 

```{r}
run(dmt01, syn_data, lbl_overall = NULL)
```

#### **3. Demographics and Baseline Characteristics with an additional study specific continuous variable**

1) Study specific continuous variables can be added to the standard demographics and baseline characteristics summary by editing the parameter `summaryvars`. To add or remove analyses, you need to list all variables you would like to include in the parameter.  
2) CHEVRON performs the analysis based on the type of variable as defined in the input data.    

```{r}
run(dmt01, syn_data, summaryvars = c("AGE", "AGEGR1", "SEX", "ETHNIC", "RACE", "BBMISI"), lbl_overall = NULL)
```

#### **4. Demographics and Baseline Characteristics with an additional study specific categorical variable**

1) Study specific categorical variables can be added to the standard demographics and baseline characteristics summary by editing the parameter `summaryvars`.   
2) To display the values within a categorical variable in pre-specified order, the categorical variable need to be factorized with pre-specified order provided as levels.

```{r}
proc_data <- syn_data
proc_data$adsl <- proc_data$adsl %>%
  mutate(
    SEX = reformat(.data$SEX, rule(Male = "M", Female = "F")),
    BBMIGR1 = factor(case_when(
      BBMISI < 15 ~ "Very severely underweight",
      BBMISI >= 15 & BBMISI < 16 ~ "Severely underweight",
      BBMISI >= 16 & BBMISI < 18.5 ~ "Underweight",
      BBMISI >= 18.5 & BBMISI < 25 ~ "Normal (healthy weight)",
      BBMISI >= 25 & BBMISI < 30 ~ "Overweight",
      BBMISI >= 30 & BBMISI < 35 ~ "Obese Class I (Moderately obese)",
      BBMISI >= 35 & BBMISI < 40 ~ "Obese Class II (Severely obese)",
      BBMISI >= 40 ~ "Obese Class III (Very severely obese)"
    ), levels = c(
      "Very severely underweight",
      "Severely underweight",
      "Underweight",
      "Normal (healthy weight)",
      "Overweight",
      "Obese Class I (Moderately obese)",
      "Obese Class II (Severely obese)",
      "Obese Class III (Very severely obese)"
    ))
  )

run(dmt01, proc_data, summaryvars = c("AGE", "AGEGR1", "SEX", "ETHNIC", "RACE", "BBMIGR1"), auto_pre = FALSE)
```

#### **5. Demographics and Baseline Characteristics with additional vital signs baseline values from `ADVS` or `ADSUB`**

To add baseline vital signs or other baseline characteristics to the demographics and baseline characteristics summary, manual preprocess of input `adsl` dataset is expected and merge the vital signs baseline values from `advs` (where `ADVS.ABLFL == "Y"`) or `adsub` with `adsl` by unique subject identifier.

```{r}
proc_data <- syn_data
diabpbl <- proc_data$advs %>%
  filter(ABLFL == "Y" & PARAMCD == "DIABP") %>%
  mutate(DIABPBL = AVAL) %>%
  select("STUDYID", "USUBJID", "DIABPBL")

proc_data$adsl <- proc_data$adsl %>%
  mutate(SEX = reformat(.data$SEX, rule(Male = "M", Female = "F"))) %>%
  left_join(diabpbl, by = c("STUDYID", "USUBJID"))

run(dmt01, proc_data, summaryvars = c("AGE", "AGEGR1", "SEX", "ETHNIC", "RACE", "DIABPBL"), auto_pre = FALSE)
```

### **Patient Disposition (`DST01`)**

#### **1. Patient Disposition**

1) The **`dst01`** template produces the standard patient disposition summary.  
2) The template includes the column of total by default. Use `lbl_overall = NULL` to suppress the default.   

```{r}
run(dst01, syn_data, lbl_overall = NULL)
```

#### **2. Patient Disposition (with grouping of reasons)**

1) The syntax below produces the standard patient disposition summary with grouping of the discontinuation reasons.  
2) The variable [`ADSL.DCSREASGP`] that groups the discontinuation reasons needs to be derived manually and provided in the input `adsl` dataset. 

```{r}
run(dst01, syn_data, detail_vars = list(Discontinued = c("DCSREASGP", "DCSREAS")), lbl_overall = NULL)
```

#### **3. Patient Disposition (adding end of treatment status)**

The syntax below adds the end of treatment status to the standard patient disposition summary by providing the end of treatment status variable to the parameter `trt_status_var`.

```{r}
run(dst01, syn_data, trt_status_var = "EOTSTT", lbl_overall = NULL)
```

#### **4. Patient Disposition (adding details of study ongoing status)**

The syntax adds the details of study ongoing/alive status to the standard patient disposition summary by modifying the parameter `detail_vars`.

```{r}
run(dst01, syn_data, detail_vars = list(Discontinued = "DCSREAS", Ongoing = "STDONS"))
```

### **Deaths (`DTHT01`)**

#### **1. Deaths**

The **`dtht01`** template produces the standard deaths output.

```{r}
run(dst01, syn_data)
```

#### **2. Deaths (adding "Primary Cause of Death" details for 'Other' category)**

```{r}
run(dtht01, syn_data, other_category = TRUE)
```

NOTE: In order to avoid the warning above and display 'Other' as the last category under "Primary Cause of Death" right above the detailed reasons for "Other", the user is expected to manually provide levels to `ADSL.DTHCAT` based on categories available in the dataset.

#### **3. Deaths (adding summary by days from last study drug administration)**

Setting `time_since_last_dose` to `TRUE`, the syntax produces the count of deaths by days from last study drug administration as well as the count of deaths by primary cause and days from last study drug administration.

```{r}
run(dtht01, syn_data, time_since_last_dose = TRUE)
```

### **ECG Results and Change from Baseline by Visit (`EGT01`)**

#### **1. ECG Results and Change from Baseline by Visit**

The **`egt01`** template produces the standard ECG results and change from baseline by visit summary.

```{r}
run(egt01, syn_data)
```

### **ECG Abnormalities (Regardless of Abnormality at Baseline) (`EGT02_1`)**

#### **1. ECG Abnormalities (Regardless of Abnormality at Baseline)**

The **`egt02_1`** template produces the standard ECG abnormalities summary where the abnormalities are summarized regardless of the abnormality at baseline.

```{r}
run(egt02_1, syn_data)
```

### **ECG Abnormalities (Among Subject Without Abnormality at Baseline) (`EGT02_2`)**

#### **1. ECG Abnormalities (Among Subject Without Abnormality at Baseline)**

The **`egt02_2`** template produces the standard ECG abnormalities summary where the abnormalities are summarized among subject without abnormality at baseline.

```{r}
run(egt02_2, syn_data)
```

### **Shift Table of ECG Interval Data - Baseline versus Minimum/Maximum Post-Baseline (`EGT03`)**

#### **1. Shift Table of ECG Interval Data - Baseline versus Minimum Post-Baseline**

The **`egt03`** template produces the standard shift table of ECG interval data - baseline versus minimum post-baseline summary.

```{r}
proc_data <- log_filter(syn_data, PARAMCD == "HR", "adeg")
run(egt03, proc_data)
```

#### **2. Shift Table of ECG Interval Data - Baseline versus Maximum Post-Baseline**

To produce the standard shift table of ECG interval data - baseline versus maximum post-baseline summary....TBA

### **ECG Actual Values and Changes from Baseline by Visit (`EGT05_QTCAT`)**

#### **1. ECG Actual Values and Changes from Baseline by Visit**

The **`egt05_qtcat`** template produces the standard ECG actual values and changes from baseline by visit summary.

```{r}
run(egt05_qtcat, syn_data)
```

#### **2. ECG Actual Values and Changes from Baseline by Visit (removing default analyses)**

The template have two default analyses of `ADEG.AVALCAT1` and `ADEG.CHGCAT1`. To keep only the analyses needed, this can be achieved by modifying the parameter `summaryvars`.

```{r}
run(egt05_qtcat, syn_data, summaryvars = c("AVALCAT1"))
```

### **Study Drug Exposure (`EXT01`)**

#### **1. Study Drug Exposure**

1) The **`ext01`** template displays total number of doses administered and total dose administered by default
2) The template does not include the column of total by default

```{r}
run(ext01, syn_data)
```

### **Laboratory Test Results and Change from Baseline by Visit (`LBT01`)**

#### **1. Laboratory Test Results and Change from Baseline by Visit**

1) The **`lbt01`** template produces the standard laboratory test results and change from baseline by visit.  
2) To select the SI/CV/LS results and the panel (chemistry/hematology/urinalysis/coagulation etc.) to display, user defines individual filters and apply to input datasets prior to running CHEVRON.  

```{r}
t_lb_chg <- run(lbt01, syn_data)
head(t_lb_chg, 20)
```

#### **2. Laboratory Test Results and Change from Baseline by Visit (customized precision)**
TBA

### **Laboratory Abnormalities (`LBT04`)**

#### **1. Laboratory Abnormalities**
1) The **`lbt04`** template produces the standard laboratory abnormalities summary.  
2) The template subsets to SI results by default.   
3) The laboratory tests and directions of abnormality in this template is data-driven. Table entries provide the number of patients with a during treatment laboratory value abnormality in the direction specified among patients without this abnormality at baseline.

```{r}
run(lbt04, syn_data)
```

### **Laboratory Abnormalities with Single and Replicated Marked (`LBT05`)**

#### **1. Laboratory Abnormalities with Single and Replicated Marked**

1) The **`lbt05`** template produces the standard laboratory abnormalities summary for marked abnormalities.  
2) The laboratory tests and directions of abnormality in this template is currently data-driven. The standard metadata for Safety Lab Standardization will be incorporated in future release.

```{r}
#run(lbt05, syn_data)
```

#### **2. Laboratory Abnormalities with Single and Replicated Marked showing all categories**

#### **3. Laboratory Abnormalities with Single and Replicated Marked with study specific `MLAs`**

### **Laboratory Abnormalities by Visit and Baseline Status (`LBT06`)**

#### **1. Laboratory Abnormalities by Visit and Baseline Status**

1) The **`lbt06`** template produces the standard laboratory abnormalities by visit and baseline status summary.

```{r}
run(lbt06, syn_data)
```

### **Laboratory Test Results with Highest `NCI CTCAE` Grade Post-Baseline (`LBT07`)**

#### **1. Laboratory Test Results with Highest `NCI CTCAE` Grade Post-Baseline**

1) The **`lbt07`** template produces the standard laboratory test results with highest `NCI CTCAE` grade post-baseline summary.  
2) The laboratory tests and grades in this template is currently data-driven. The standard metadata for possible lab tests and corresponding `NCI CTCAE` grade will be incorporated in future release.

```{r}
run(lbt07, syn_data)
```

### **Laboratory Test Results Shift Table - Highest `NCI-CTCAE` Grade Post-Baseline by Baseline `NCI-CTCAE` Grade (`LBT14`)**

#### **1. Laboratory Test Results Shift Table - Highest `NCI-CTCAE` Grade Post-Baseline by Baseline `NCI-CTCAE` Grade (High)**

To produce the standard laboratory test results shift table - highest `NCI-CTCAE` grade post-baseline by baseline `NCI-CTCAE` grade summary for high abnormalities, use the **`lbt14`** template and set the parameter *`direction`* to `high`.

```{r}
run(lbt14, syn_data, direction = "high")
```

#### **2. Laboratory Test Results Shift Table - Highest `NCI-CTCAE` Grade Post-Baseline by Baseline `NCI-CTCAE` Grade (Low)**

To produce the standard laboratory test results shift table - highest `NCI-CTCAE` grade post-baseline by baseline `NCI-CTCAE` grade summary for high abnormalities, use the **`lbt14`** template and the parameter `direction` is `low` by default.

```{r}
run(lbt14, syn_data)
```

#### **3. Laboratory Test Results Shift Table - Highest `NCI-CTCAE` Grade Post-Baseline by Baseline `NCI-CTCAE` Grade (High) Without Patients with Missing Baseline**

To exclude patients with missing baseline grade, set the parameter `gr_missing` to `excl`.

```{r}
run(lbt14, syn_data, direction = "high", gr_missing = "excl")
```

#### **4. Laboratory Test Results Shift Table - Highest `NCI-CTCAE` Grade Post-Baseline by Baseline `NCI-CTCAE` Grade (Low) with Missing Baseline Considered as Grade 0**

To count patients with missing baseline grade as grade 0, set the parameter `gr_missing` to `gr_0`.

```{r}
run(lbt14, syn_data, gr_missing = "gr_0")
```

#### **4. Laboratory Test Results Shift Table - Highest `NCI-CTCAE` Grade Post-Baseline by Baseline `NCI-CTCAE` Grade (with fill in of grades)**

To display all possible grades even if they do not occur in the data, set the parameter `prune_0` to `FALSE`.

```{r}
run(lbt14, syn_data, direction = "high", prune_0 = FALSE)
```

### **Medical History (`MHT01`)**

#### **1. Medical History**

1) The **`mht01`** template displays medical conditions by MedDRA system organ class and Preferred Name by default.    
2) The default treatment variable is `ADSL.ARM`.   
3) The user is expected to use filter to subset medical conditions prior to or on entering study.  
4) By default, the template produces the overall 'total number of conditions' as well as the 'total number of conditions' per body system after the summary of patients.  
5）This template currently does not support sorting MedDRA system organ class and preferred names by order of frequency.

```{r}
run(mht01, syn_data)
```

#### **2. Medical History showing additional column 'All Patients'**

```{r}
run(mht01, syn_data, lbl_overall = "All Patients")
```

### **Duration of Exposure for Risk Management Plan (`RMPT01`)**

#### **1. Duration of Exposure for Risk Management Plan**

The **`rmpt01`** template produces the standard duration of exposure output for the Risk Management Plan (`RMP`).

Person time is the sum of exposure across all patients in days.

```{r}
run(rmpt01, syn_data)
```

### **Extent of Exposure by Age Group and Gender for Risk Management Plan (`RMPT03`)**

#### **1. Extent of Exposure by Age Group and Gender for Risk Management Plan**

The **`rmpt03`** template produces the standard extent of exposure by age group and gender output for the Risk Management Plan (`RMP`).

By default, the `AGEGR1` variable is used as the age group. If `AGEGR1` is available in `ADSL` only but not in `ADEX`, it needs to be added to `ADEX` first.

```{r}
proc_data <- syn_data
proc_data <- propagate(proc_data, "adsl", "AGEGR1", "USUBJID")
run(rmpt03, proc_data)
```

Any other study specific age group can be used by editing the parameter `summaryvars`. For all `RMP` tables, if the variable specified per `summaryvars` is unavailable in `ADEX`, it needs to be added to `ADEX` first.
```{r}
proc_data <- syn_data
proc_data$adsl <- proc_data$adsl %>%
  mutate(
    AGEGR2 = with_label(
      factor(case_when(
        AAGE < 18 ~ "<18",
        AAGE >= 18 & AAGE <= 65 ~ "18 - 65",
        AAGE > 65 ~ ">65",
      ), levels = c("<18", "18 - 65", ">65")),
      "Age Group 2"
    )
  )
proc_data <- propagate(proc_data, "adsl", "AGEGR2", "USUBJID")
run(rmpt03, proc_data, summaryvars = "AGEGR2")
```

### **Extent of Exposure by Ethnic Origin for Risk Management Plan (`RMPT04`)**

#### **1. Extent of Exposure by Ethnic Origin for Risk Management Plan**

The **`rmpt04`** template produces the standard extent of exposure by ethnic origin output for the Risk Management Plan (`RMP`).

```{r}
run(rmpt04, syn_data)
```

### **Extent of Exposure by Race for Risk Management Plan (`RMPT05`)**

#### **1. Extent of Exposure by Race for Risk Management Plan**

The **`rmpt05`** template produces the standard extent of exposure by race output for the Risk Management Plan (`RMP`).

```{r}
run(rmpt05, syn_data)
```

### **Vital Signs (`VST01`)**

#### **1. Vital Sign Results and Change from Baseline by Visit**

```{r}
t_vs_chg <- run(vst01, syn_data)
head(t_vs_chg, 20)
```

### **Vital Signs Abnormalities (Regardless of Abnormality at Baseline) (`VST02_1`)**

#### **1. Vital Sign Abnormalities (Regardless of Abnormality at Baseline)**

```{r}
run(vst02_1, syn_data)
```

### **Vital Signs Abnormalities (Among Subject Without Abnormality at Baseline) (`VST02_2`)**

#### **1. Vital Sign Abnormalities (Among Subject Without Abnormality at Baseline)**

```{r}
run(vst02_2, syn_data)
```


### **Cox Regression (`COXT01`)**

#### **1. Cox Regression**

The **`coxt01`** template produces the standard cox regression output.

```{r}
proc_data <- log_filter(syn_data, PARAMCD == "CRSD", "adtte")
proc_data <- log_filter(proc_data, ARMCD != "ARM C", "adsl")
proc_data$adtte$ARM <- droplevels(proc_data$adtte$ARM)
run(coxt01, proc_data)
```


#### **2. Cox Regression with Interaction Term**

To add interaction term to the models, the parameter `interaction` can be set to `TRUE`.

```{r}
run(coxt01, proc_data, interaction = TRUE)
```

#### **3. Cox Regression (Specifying Covariates)**

The covariates to be included in the models can be specified by the parameter `covariates`. 

```{r}
run(coxt01, proc_data, covariates = c("ETHNIC", "AAGE"))
```

#### **4. Cox Regression (Setting Strata, Ties, and Alpha Level)**

The strata used in the models can be specified by the parameter `strata`. The method used to handle ties can be set by the parameter `ties`. The confidence level can be set by parameter `conf_level`. 


```{r}
run(coxt01, proc_data, covariates = c("SEX", "AAGE"), strata = c("RACE"), ties = "exact", 
    conf_level = 0.90)
```


### **Multi-variable Cox Regression (COXT02)**

#### **1. Multi-variable Cox Regression**

The `coxt02` template produces the standard multi-variable cox regression output.


```{r}
proc_data <- log_filter(syn_data, PARAMCD == "CRSD", "adtte")
run(coxt02, proc_data)
```


#### **2. Multi-variable Cox Regression (with Interaction) - is this kept in chevron?**



```{r}
run(coxt02, proc_data, interaction = TRUE)
```


#### **3. Multi-variable Cox Regression (Specifying Covariates)**

The covariates to be included in the model can be specified by parameter `covariates`.

```{r}
run(coxt02, proc_data, covariates = c("SEX", "AAGE"))
```



#### **4. Multi-variable Cox Regression (specifying covariates from adsub) - is this kept in chevron?**

#### **5. Multi-variable Cox Regression (Setting Strata, Ties, Alpha Level, and Statistics)**

The strata used in the models can be set by parameter `strata`. 
The confidence level used in the models can be set by parameter `conf_level`.

```{r}
run(coxt02, proc_data, covariates = c("SEX", "AAGE"), strata = c("RACE"), conf_level = 0.90)
```

#### **6. Multi-variable Cox Regression (with selection process for covariates) - how to achieve this in chevron?**


### **Overview of the Actual Measurements and Their Changes from Baseline Over the Course of the Trial (`CFBT01`)**

#### **1. Overview of Actual Measurements and Their Changes from Baseline Over the Course of the Trial**

The `cfbt01` template generates the output that provides an overview of actual measurement values and the changes from baseline over the course of the trial. 

```{r}
 proc_data <- log_filter(
   syn_data,
   PARAMCD %in% c("DIABP", "SYSBP"), "advs"
 )

run(cfbt01, proc_data, dataset = "advs")
```



### **Major Protocol Deviations (`PDT01`)**

#### **1. Major Protocol Deviations**

The `pdt01` template produces the standard major protocol deviations output.

```{r}
proc_data <- syn_data
proc_data$addv <- proc_data$addv %>%
  filter(DVCAT == "MAJOR")

run(pdt01, proc_data)
```

### **Reasons for Major Protocol Deviations Related to Epidemic/Pandemic (`PDT02`)**

#### **1. Reasons for Major Protocol Deviations Related to Epidemic/Pandemic**

The `pdt02` template produces the reasons for major protocol deviations related to epidemic/pandemic summary.

```{r}
run(pdt02, syn_data)
```


### **Best Overall Response (`RSPT01`)**

#### **1. Best Overall Response**

The `rspt01` template produces the standard best overall response output.

```{r}
proc_data <- log_filter(syn_data, PARAMCD == "BESRSPI", "adrs")
run(rspt01, proc_data)
```


#### **2. Best Overall Response (selecting sections to display)**

The odds ratio section can be excluded from the output by setting the parameter `odds_ratio` to `FALSE`.

```{r}
run(rspt01, proc_data, odds_ratio = FALSE)
```

#### **3. Best Overall Response (modifying analysis details like type of confidence interval, alpha level, test for p-value)**

The methods to be applied in the analysis can be set through the `methods` parameter. Allowed methods include `diff_pval_method`, `diff_conf_method`, `strat_diff_conf_method` (for stratified analysis), and `strat_diff_pval_method` (for stratified analysis).

The confidence level to be applied in the analysis can be set through the `conf_level` parameter. 

```{r}
run(rspt01, proc_data, methods = list(diff_pval_method = "fisher",
                                      diff_conf_method = "wald",
                                      strat_diff_conf_method = "ha",
                                      strat_diff_pval_method = "schouten"), 
    conf_level = 0.90)
```


#### **4. Best Overall Response (with stratified analysis)**

The `perform_analysis` parameter can be altered to conduct the analysis as stratified (`strat`), unstratified (`unstrat`), or both (`c("unstrat", "strat)`). 

```{r}
run(rspt01, proc_data, perform_analysis = c("unstrat", "strat"),
    strata = c("STRATA1", "STRATA2"))
```

#### **5. Best Overall Response (modifying the definition of overall response) - how to do this?**
#### **6. Best Overall Response (define new sections to display) - how to do this?**


### **Time-to-event Summary (`TTET01`)**

#### **1. Time-to-event Summary**

The `ttet01` template produces the standard time-to-event summary.

```{r}
proc_data <- log_filter(syn_data, PARAMCD == "PFS", "adtte")
run(ttet01, proc_data)
```

#### **2. Time-to-event Summary (selecting sections to display) - how to do this?**

```{r}
run(ttet01, proc_data,
   summarize_event = FALSE)
```

#### **3. Time-to-event Summary (modifying analysis details like conftype, ties, alpha level)**

The confidence interval type can be set by parameter `conf_type`.

The method applied to handle ties can be controlled by parameter `ties`.

The confidence level applied can be controlled by parameter `conf_level`.

The p-value method for testing hazards ratio = 1 can be set by parameter `pval_method`.

The method of the analysis can be set through parameter `method`, with options either `"surv"` (survival estimations),
`"surv_diff"` (difference in survival with the control) or `"both"`.


```{r}
run(ttet01, proc_data,
   summarize_event = FALSE, conf_type = "log-log", ties = "exact", conf_level = 0.90, 
   pval_method = "likelihood", method = "both")
```


#### **4. Time-to-event Summary (with stratified analysis)**

The parameter `perform_analysis` can be set to conduct the analysis as stratified (`strat`), unstratified (`unstrat`) or both (`c("unstrat", "strat")`). 

```{r}
 run(ttet01, proc_data,
     perform_analysis = c("unstrat", "strat"),
     strata = c("STRATA1", "STRATA2"))
```


#### **5. Time-to-event Summary (modifying time point for the “xx year duration” analysis)**

The timepoint of interest can be set through the `timepoint` parameter. 

```{r}
 run(ttet01, proc_data,
     timepoint = 180)
```


#### **6. Time-to-event Summary (requesting more than one p-value) - is it allowed?**

```{r}
run(ttet01, proc_data,
    pval_method = "likelihood")
```





## **LISTINGS**

### **Glossary of Adverse Event Preferred Terms and Investigator-Specified Terms (`AEL01_NOLLT`)**

#### **1. Glossary of Adverse Event Preferred Terms and Investigator-Specified Terms**

1) The **`ael01_nollt`** template produces the standard glossary of adverse event preferred terms and investigator-specified terms.
2) The example below use `head` function to print only the first 10 lines of the output.

```{r}
l_ae_nollt <- run(ael01_nollt, syn_data)
head(l_ae_nollt, 10)
```




## **GRAPHS**

### **Subgroup Analysis of Best Overall Response (`FSTG01`)**

#### **1. Subgroup Analysis of Best Overall Response**

The `fstg01` template produces the standard subgroup analysis of best overall response graphic.


```{r}
proc_data <- log_filter(
   syn_data,
   PARAMCD == "BESRSPI" & ARM %in% c("A: Drug X", "B: Placebo"), "adrs"
 )

run(fstg01, proc_data,
   dataset = "adrs"
 )
```


#### **2. Subgroup Analysis of Best Overall Response (specifying class variables and options for the treatment variable)**

The subgroups applied in the analysis can be set by the parameter `subgroups`.

```{r}
run(fstg01, proc_data,
   subgroups = c("SEX"),
   dataset = "adrs")
```


#### **3. Subgroup Analysis of Best Overall Response (changing the alpha level)**

The confidence level applied in the analysis can be set through parameter `conf_level`.

```{r}
run(fstg01, proc_data,
   conf_level = 0.90,
   dataset = "adrs")
```


#### **4. Subgroup Analysis of Best Overall Response (modify plot options)**

The plot options can be controlled by passing additional arguments that are included in `tern::g_forest()` to the call.

```{r}
run(fstg01, proc_data,
   col = "brown", 
   col_symbol_size = 1.5,
   dataset = "adrs")
```

#### **5. Subgroup Analysis of Best Response of CR/PR (setting values indicating response) - how to do this?**

### **Kaplan-Meier Plot**

#### **1. Kaplan-Meier Plot (`KMG01`)**

The `kmg01` template produces the standard Kaplan-Meier plot.


```{r}
proc_data <- log_filter(syn_data, PARAMCD == "AEREPTTE", "adaette")
run(kmg01, proc_data, dataset = "adaette")
```

#### **2. Kaplan-Meier Plot (Plotting Failure)**

```{r}
run(kmg01, proc_data, dataset = "adaette", yval = "Failure")
```

#### **3. Kaplan-Meier Plot (with comparative statistics)**

To display the comparative statistics, the argument `annot_coxph` can be set to `TRUE`.

```{r}
run(kmg01, proc_data, datasets = "adaette", annot_coxph = FALSE)
```

#### **4. Kaplan-Meier Plot (without censoring marks)**

The censoring marks can be hidden by setting the parameter `censor_show` to `FALSE`.

```{r}
proc_data <- log_filter(syn_data, PARAMCD == "OS", "adtte")
run(kmg01, proc_data, dataset = "adtte", censor_show = FALSE)
```

#### **5. Kaplan-Meier Plot (modifying plot appearances)**

The Kaplan-Meier plot aesthetics can be modified by modifying the following parameters:

- `col` : controls the colors of each group.
- `pch` : controls the shape of the censor marks.
- `annot_coxph` : controls whether to show an annotation table from cox regression or not.
- `annot_stats` : controls the statistic annotations to be added to the plot.

More arguments from `tern::g_km` can be included. 


```{r}
col <- c(
   "A: Drug X" = "black",
   "B: Placebo" = "blue",
   "C: Combination" = "gray"
)

proc_data <- log_filter(syn_data, PARAMCD == "OS", "adtte")
run(kmg01, proc_data, dataset = "adtte", line_col = col, pch = 1, 
    annot_coxph = TRUE, annot_stats = "min")
```

#### **6. Kaplan-Meier Plot (modifying options for statistics, ties handling, stratification, …)**

The p-value method for testing hazard ratio = 1 can be altered by changing parameter `pval_method`.

The method to be applied to handle ties can be controlled by `ties`.

The confidence level to be applied in the analysis can be set by parameter `conf_level`.

The strata to be applied in the analysis can be set by parameter `strat`. 


```{r}
proc_data <- log_filter(syn_data, PARAMCD == "OS", "adtte")
run(kmg01, proc_data, dataset = "adtte", pval_method = "likelihood", 
    ties = "exact", 
    annot_coxph = TRUE, 
    conf_level = 0.90, 
    strat = "SEX")
```


### **Mean Plot (`MNG01`)**

#### **1. Plot of Mean and Confidence Interval**

The `mng01` template produces the mean plot graphical output that's an overview of a summary statistics across time and arm for a selected data set.

```{r}
run(mng01, syn_data, dataset = "adlb")
```

#### **2. Plot of Mean and Confidence Intervals of Change from Baseline of Vital Signs (Changing the Input Analysis Data Set and Analysis Variable) - how to do this?**

The analysis variables can be set through the following parameters:
- `x_var` controls the variable(s) to be shown on the x-axis (multiple values allowed).
- `y_var` cnotrols the variable to be shown on the y-axis (only allows single value).


```{r}
#run(mng01, syn_data, dataset = "adlb", x_var = c("AVISIT", "AVISITN"), y_var = "CHG", y_name = "CHG")
```

#### **3. Plot of Mean (+/-SD) (Changing the Statistics)**

The statistics computed can be altered through parameters:

- `center_fun` controls the function to estimate value.
- `interval_fun` controls the function to define the crossbar range. 


```{r}
run(mng01, syn_data, dataset = "adlb", 
    center_fun = "median", 
    interval_fun = "median_ci")
```

#### **4. Plot of Mean and Confidence Interval (Modify Alpha Level) - how to do this?**


```{r}
run(mng01, syn_data, dataset = "adlb", conf_level = 0.90)
```

#### **5. Plot of Mean and Confidence Interval (Customize Table Output)**

- The summary table can be excluded from the output by setting `show_table` to `FALSE`.

```{r}
run(mng01, syn_data, dataset = "adlb", show_table = FALSE)
```

- The number of observations can be excluded from the output by setting `show_n` to `FALSE`.

```{r}
run(mng01, syn_data, dataset = "adlb", show_n = FALSE)
```

#### **6. Plot of Median and Confidence Interval (Condense Visits in Table Section) - how to do this?**


#### **7. Plot of Mean and Upper Confidence Limit - how to do this?**

```{r}
run(mng01, syn_data, dataset = "adlb")
```

#### **8. Plot of Mean and Confidence Interval (Customize Plot Appearance)**

The colors of the lines can be customized by parameter `line_col`.
The background horizontal grid can be hidden by setting `show_h_grid` to `FALSE`. 
The background vertical grid can be hidden by setting `show_v_grid` to `FALSE`.
The dodge distance between groups can be altered by parameter `jitter`.


```{r}
col <- c(
   "A: Drug X" = "black",
   "B: Placebo" = "blue",
   "C: Combination" = "gray"
 )
run(mng01, syn_data, dataset = "adlb", line_col = col,
    show_h_grid = FALSE, show_v_grid = FALSE, jitter = 0.5)
```


