---
title: "Introduction to Chevron"
date: "`r Sys.Date()`"
author: Adrian Waddell
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Chevron}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Introduction 

The `chevron` R package provides functions to produce standard tables, listings and graphs (TLGs) used to analyze and
report clinical trials data. We refer to these functions as *tlg-functions*. The *tlg-functions* in `chevron` use other
packages to produce the final outputs, for example `rtables` and `tern` are used to create listings and tables, and
`ggplot2`, `lattice`, and `grid` are used to create graphs.


*tlg-functions* in `chevron` such as `dmt01_1`, `aet02_1`, `aet02_2` have the following properties:

1. they produce a narrow defined output (currently standards in Roche GDS). Note, that the naming convention 
   `<gds template id>_<i>` indicates that a Roche GDS defined standard may have different implementations. Or,
    alternatively, a GDS template id can be regarded as a *guideline* and the function name in `chevron` as a
    *standard*.
1. have very few arguments to modify the standard. Generally, arguments may change the structure of the table (arm
variable, which variables are summarized) but not parameterize the cell content (i.e. alpha-level for p-value).
1. have always the first argument `adam_db` which is the collection of ADaM datasets (`ADSL`, `ADAE`,
`ADRS`, etc.). Please read the *The adam_db Argument* vignette in this package for more details.
1. have a `.study` argument, read the *The .study argument* vignette for more detail.

## Example AET02

For example, the GDS template `aet02` is implemented in `chevron` with *tlg-functions* that have the name `aet02_*`. The
function documentation which is accessible with the `help` function, e.g. `help('aet02_1')` documents what is particular
in the `_1` implementation.

We first define the data and put it in a `dm` object, you can find more details about this in the *adam_db* vignette.

```{r}
library(dm)
library(scda)

syn_data <- synthetic_cdisc_data("latest")

adam_study_data <- dm(adsl = syn_data$adsl, adae = syn_data$adae) %>%
  dm_add_pk(adsl, c("USUBJID", "STUDYID")) %>%
  dm_add_fk(adae, c("USUBJID", "STUDYID"), ref_table = "adsl") %>%
  dm_add_pk(adae, c("USUBJID", "STUDYID", "ASTDTM", "AETERM", "AESEQ"))

validate_dm(adam_study_data)
```

A the `aet02_1` output is then created as follows:

```{r}
library(chevron)

db <- adam_study_data %>%
  (std_filter("aet02_1"))() %>%
  (std_mutate("aet02_1"))() 

aet02_1(adam_db = db)
```

Note that

* the `std_filter` and `std_mutate` are bundled with `aet02_1` and often return the `identity` function but sometimes
contain modifications that do not belong to the ADaM model. For example, here

   ```{r}
   std_filter("aet02_1")
   ```

* the functions returned by `std_mutate` and `std_filter` has always the first argument `adam_db` and might have optional arguments, including possibly the `.study` object.
* the `tlg-function` in `chevron` also return the standard titles and footnotes

