---
title: "Script_Generator"
author: Benoit Falquet
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Script_Generator}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options:
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(chevron)
library(dplyr)
```

## Introduction

In addition of the embedded `run()` method to create a `tlg`, chevron offers a script-based approach that allows the
user to quickly edit a chevron workflow without the need for modifying a `chevron_tlg` object.
The script is generated from `script_funs` method which by default only output the script corresponding to the
preprocessing function in the generated script.

## Using a chevron-defined object

The object returned by the `script` methods are vectors of character with one element per line of the script, that can be easily rendered.

```{r}
res <- script_funs(aet01, adam_db = "syn_data", args = "args_list")
writeLines(res)
```

## With a modified chevron object

The script generator depends on the functions actually stored in the object. Modifying the `chevron_tlg` object can lead to a different script.

```{r}
aet01_custom <- aet01
preprocess(aet01_custom) <- function(adam_db, new_format, ...) {
  reformat(adam_db, new_format)
}

res_funs <- script_funs(aet01_custom, adam_db = "syn_data", args = "args_list")
```

Print the generated scripts. Note that a new argument `new_format` has been added and the pre processing function has been modified.

```{r}
writeLines(res_funs)
```
