---
title: "TLG pipelines"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The .study Argument}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Introduction 

The idea behind the `TLG pipeline` object is to offer the user a decentralized way to easily combine pre processing and `tlg` function with metadata information. The resulting object 

# Usage

## Predefined Pipeline

Chevron stores predefined pipelines ready to use. To run the entire pipeline:

```{r}

# aet01_1$run(adam_data)

# .study <- list(
#   actualarm = "ACTARM",
#   lbl_overall = NULL,
#   safety_var = c(
#     "FATAL", "SER", "SERWD", "SERDSM",
#     "RELSER", "WD", "DSM", "REL", "RELWD", "RELDSM", "SEV"
#   )
# )

# aet01_1$run(adam_data, .study = .study, armvar = "ARM")


```

## Customize Pipeline

Available slots

```{r}




# aet01_1$reset()

```


## Create Pipeline

NULL original

```{r}




```





